### 2024-05-15 sections/4-results.tex
RadioML not scale free
address radioml sampling

Relative to the other datasets, RadioML, as displayed in Figure~\ref{fig:results:radioml-lfd}, exhibits high LFD.
Notably, however, for the first approximately 15 depths, the 95$^{th}$ percentile and median LFD are very close to 0.
Both percentiles increase sharply after depth 20, nearly reaching 16.
LFD remains high even as depth increases, with the 95$^{th}$ percentile fluctuating between about 6 and 15 for depths about 20-40.
It then spikes up again to about 10 at around depth 45 before decreasing linearly to 1 at depth 60.
The median LFD follows a similar pattern of peaks and troughs, fluctuating between about 3 and 15 for depths 20-40, spiking at about depth 50 to 5, and then decreasing approximately linearly to 1 at depth 60.

>>>>

Relative to the other datasets, RadioML, as displayed in Figure~\ref{fig:results:radioml-lfd}, exhibits high LFD.
Notably, however, for the first approximately 15 depths, the 95$^{th}$ percentile and median LFD are very close to 0. 
Both percentiles increase sharply after depth 20, nearly reaching 16.
LFD remains high even as depth increases, with the 95$^{th}$ percentile fluctuating between about 6 and 15 for depths about 20-40.
It then spikes up again to about 10 at around depth 45 before decreasing linearly to 1 at depth 60.
The median LFD follows a similar pattern of peaks and troughs, fluctuating between about 3 and 15 for depths 20-40, spiking at about depth 50 to 5, and then decreasing approximately linearly to 1 at depth 60. The inconsistency of LFD in the RadioML dataset suggests that it obeys the manifold hypothesis at some scales, but that it is not ``scale free,'' as the LFD varies significantly by depth; this could be due to dense sampling or -- as this is still a synthetic dataset -- nonuniform generation of data. Silva, in contrast, appears to obey the manifold hypothesis at all scales.
